XOR-Some Prolific Pilot 2

### 2021-04-05 analysis/xor-some-prolific-pilot2.Rmd
add rating deviations

```{r, echo=FALSE}
d_critical_clean <- d_full_clean %>% filter(condition == "critical")
d_critical_long <- d_critical_clean %>% 
  pivot_longer(c(competence, relevance, prior), 
               names_to = "class_condition", 
               values_to = "prior_class")
```

@@

d_critical_long <- d_critical_long %>% 
  mutate(w_utterance = ifelse(is.na(critical_question), F, T),
         block = ifelse(block == "comp", "competence", 
                        ifelse(block == "rel", "relevance", ifelse(block == "pri", "prior", block) )))
d_critical_long %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  group_by(main_type, class_condition, w_utterance, prior_class) %>% 
  summarize(mean_response = mean(response)) -> d_critical_summary

@@

```
Create more extensive condition labels, including information about whether a rating was produced with or without the utterance given.

>>>>

```{r, echo=FALSE}
d_critical_clean <- d_full_clean %>% filter(condition == "critical")
d_critical_long <- d_critical_clean %>% 
  pivot_longer(c(competence, relevance, prior), 
               names_to = "class_condition", 
               values_to = "prior_class")

d_critical_long <- d_critical_long %>% 
  mutate(w_utterance = ifelse(is.na(critical_question), F, T),
         block = ifelse(block == "comp", "competence", 
                        ifelse(block == "rel", "relevance", ifelse(block == "pri", "prior", block) )))
```

Create more extensive condition labels, including information about whether a rating was produced with or without the utterance given.

Average nr of responses per question per vignette:
```{r}
d_critical_long %>% 
  filter(class_condition == block | block == "xor" | block == "some") %>%
  select(-class_condition, -prior_class) %>%
  unique() %>% count(title, block_extended, main_type) %>%
  mutate(n = ifelse(main_type == "xor" & block_extended == "prior", n/2, n)) %>%
  summarize(mean_observations = mean(n))
```

Compute the average deviation from expected responses for each vignette, individually for each dimension (rel / comp / pri):
```{r}
d_critical_long %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  mutate(expected_rating = prior_class * 100,
         response_deviation = abs(response - expected_rating)) %>%
  group_by(title, block_extended) %>%
  summarize(mean_deviation = mean(response_deviation)) %>%
  arrange(desc(mean_deviation), .by_group = T) %>%
  # get the largest deviations - over 50 
  filter(mean_deviation >= 50) -> d_critical_deviations

#d_critical_deviations %>% write_csv("../data/pilots/pilot2_byItem_rating_deviations.csv")

print(d_critical_deviations)

# count which dimension is the most problematic - the prior
d_critical_deviations %>% group_by(block_extended) %>% count()

# check which items have the most deviations over 50 
d_critical_deviations %>% group_by(title) %>% count() %>% arrange(desc(.$n))
```

@@

d_critical_long %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  group_by(main_type, class_condition, w_utterance, prior_class) %>% 
  summarize(mean_response = mean(response)) -> d_critical_summary

@@
